Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-09-07 response.md

Use of a different method such as a tree could potentially prove to be a superior separator. However, the new normalization technique used in this draft results in very clean separation based on the convex hull, with only a single adjustment (see https://github.com/willettk/gzhubble/blob/master/python/creating_debiased_catalog/STEP_3_ferengi_smooth_function.ipynb). Further optimization would have an extremely minimal effect on the overall results.

----------------------------------
Minor Comment 8
----------------------------------

***8) Section 4.2: "In each unclassifiable (shaded blue) z,mu bin, the spread of intrinsic values for f_features,z=0.3 for four ranges of observed f_features is computed." Where did the "four" come from? More explanation needed.***

We chose to evaluate the distribution of f_features in 5 (not 4; a typo in the earlier manuscript has been corrected) bins to match the common ranges of vote fractions used in previous GZ morphological studies: 0.0-0.2 is typically used to indicate weak/no detection of the feature in question, 0.2-0.4, 0.4-0.6, and 0.6-0.8 represent ranges of increasing likelihood of detection, and 0.8-1.0 represents a very strong detection. This explanation has been added to the text at the end of Section 4.1.

@@

----------------------------------
Minor Comment 9
----------------------------------

***9) Why 80% of the data (orange bars, Figure 10)? This is an ad hoc choice that doesn't correspond to any typical statistical practice (except perhaps a 10% trimmed mean, but the authors are not computing means here). And how is this information applied in Figure 11, middle panel? This is not clear.***

The threshold of 80% was initially a somewhat arbitrary choice to represent the distribution of f_features in a given bin; the authors agree with the referee that a more typical statistical range would be more appropriate. We have changed the range to upper and lower 1 sigma limits, or the inner 68% of the data. The figure (now Figure 8) has been modified and text added to the end of Section 4.1.

@@

----------------------------------
Minor Comment 10
----------------------------------

***10) Section 4.3: "The goodness-of-fit was evaluated in each bin, for each Task, using a normalized chi^2 metric." The authors need to provide the formula for this; the numbers don't make sense, if one assumes "normalized" is the same
as "reduced chi^2" (where the typical value for a good fit is approximately 1).***

We agree that the normalized chi-squared is not the ideal metric for evaluating the goodness-of-fit here. Rather than comparing the fits of the polynomials for Task 1 vs the rest of the tasks, we compare the available data per bin. For Task 1, an average of 59 points were fit in each z-mu bin (Figure 9). Fitting parameters for any other task is significantly limited by the number of galaxies in each z-mu bin; the higher-order tasks have an average of only 9 galaxies per bin. This is driven by the fact that the tasks do not meet the minimum threshold of 10 individual classifications (this threshold is exceeded for every galaxy in Task 1, however). This simpler evaluation should make it more evident to the reader that the FERENGI data was not well-fit for questions beyond Task 01.

As this is not a key product of the paper, we have removed Figures A5 and A6 from the manuscript to avoid confusion and extraneous discussion. Additional text has been added at the end of Section 4.3.

### 2016-09-07 writeup/gz_hubble_data_draft_2.tex
Removal of reduced chi^2, discussion of higher-order tasks (MiC 10).

In the \ferengi{} data, these numbers severely limit the amount of information
that can be extracted for the higher-tier questions. The debiasing technique
used (Section~\ref{ssec:zeta}) requires that at least 10~classifiers answer each
question for a galaxy with $z_\mathrm{sim}=0.3$ \emph{and} the corresponding
image at higher redshift. This requirement is (by default) met by all galaxies
for the smooth/features question. However, this is often \emph{not} met for
questions beyond Task~01. On average, $60\%\pm24\%$ of the galaxies do not have
sufficient data to measure a correction, as compared to 2.0\% achieved for
Task~01 (Table~\ref{tbl:ferengi_corrections}).\hl{This left each surface brightness/redshift bin 
with insufficient data points to fit a function with confidence; on average only 9 points
remained in each bin (as compared to an average of 59 points per bin for Task~01). For these reasons,
debiased vote fractions are only offered in the GZH catalogue for Task~01
(smooth/features).  }

@@

We repeated all analyses comparing morphologies between GZH and external
\hl{publications} on the entire GZH dataset, rather than the volume-limited sample
($z<1.0,m<22.5$) discussed above. If galaxies at all redshifts and at the
original magnitude limit of $m<23.5$ are used, the correlations between all of
the automatic morphological populations and GZH decrease significantly.  The
exceptions are the GEMS galaxies, which are the only sample that was visually
classified and had a shallower magnitude cut on their catalogue.  Based on
these comparisons, we suggest that use of morphological catalogues with these
\hst{} images be limited to galaxies with $m_\mathrm{I|i|z}<22.5$; fainter
targets have been demonstrated to be less reliable, regardless of the method of
morphological classification being used.

>>>>

In the \ferengi{} data, these numbers severely limit the amount of information
that can be extracted for the higher-tier questions. The debiasing technique
used (Section~\ref{ssec:zeta}) requires that at least 10~classifiers answer each
question for a galaxy with $z_\mathrm{sim}=0.3$ \emph{and} the corresponding
image at higher redshift. This requirement is (by default) met by all galaxies
for the smooth/features question. However, this is often \emph{not} met for
questions beyond Task~01. On average, $60\%\pm24\%$ of the galaxies do not have
sufficient data to measure a correction, as compared to 2.0\% achieved for
Task~01 (Table~\ref{tbl:ferengi_corrections}). \changes{This leaves the average
surface brightness/redshift bin 
with insufficient data points to confidently measure the change in vote fraction ($\lesssim10$~galaxies per bin). 
For these reasons, debiased vote fractions are only provided in the GZH catalogue for Task~01
(smooth/features). We suggest that use of morphological data for higher order tasks should instead use
the weighted vote fractions (see Section~\ref{sec:cookbook}).}

@@

We repeated all analyses comparing morphologies between GZH and external
\changes{publications} on the entire GZH dataset, rather than the volume-limited sample
($z<1.0,m<22.5$) discussed above. If galaxies at all redshifts and at the
original magnitude limit of $m<23.5$ are used, the correlations between all of
the automatic morphological populations and GZH decrease significantly.  The
exceptions are the GEMS galaxies, which are the only sample that was visually
classified and had a shallower magnitude cut on their catalogue.  Based on
these comparisons, we suggest that use of morphological catalogues with these
\hst{} images be limited to galaxies with $m_\mathrm{I|i|z}<22.5$; fainter
targets have been demonstrated to be less reliable, regardless of the method of
morphological classification being used.
